---
title: "Analysis and Modeling of US Pollution Data for '1980-2018'
and its implications on the atmosphere"
author: "Yash Gokhale (ysg)"
output: pdf_document

---
Importing datasets

```{r}
setwd("C:\\Users\\yashg\\OneDrive\\Desktop\\CMU\\Fall 2019\\Data Science\\Project\\")
library(readxl)
library(ggplot2)
library(tidyverse)
library(lubridate)

data<-read_csv('combined.csv')
```
Simple Regression Model for Temperature and %RH
The first regression model taken into account is the Simple Linear Regression Model for Temperature and %RH. 
```{r}
#Basic regression model
#Comparing temperature with concentrations
simplemodel_T<-lm(Avg_T~Avg_CO+Avg_NO2+Avg_O3+Avg_SO2,data=data)
summary(simplemodel_T)
```
The results of the Temperature model give out coeffs for the pollutants.
```{r}

#Comparing RH with concentrations
simplemodel_RH<-lm(Avg_RH~Avg_CO+Avg_NO2+Avg_O3+Avg_SO2,data=data)
summary(simplemodel_RH)
```
#Adding year and month
```{r}
#Basic regression model
#Comparing temperature with concentrations
simplemodel2_T<-lm(Avg_T~Avg_CO+Avg_NO2+Avg_O3+Avg_SO2+Year+Month,data=data)
summary(simplemodel2_T)
```
#Adding year and month
For RH
```{r}
#Basic regression model
#Comparing temperature with concentrations
simplemodel2_RH<-lm(Avg_RH~Avg_CO+Avg_NO2+Avg_O3+Avg_SO2+Year+Month+State_Name,data=data)
summary(simplemodel2_RH)
write.csv( tidy(simplemodel2_RH) , "coefs2.csv" )
```

We can see that the inclusion of Year and Month(as a categorical variable improves the model and the equivalent R-squared)

```{r}
library(broom)
simplemodel3_T<-lm(Avg_T~Avg_CO+Avg_NO2+Avg_O3+Avg_SO2+Year+Month+State_Name,data=data)
summary(simplemodel3_T)
write.csv( tidy(simplemodel3_T) , "coefs.csv" )
```
In order to find general trends, averaged over pollution:
```{r}
data_f<-data%>%
  group_by(State_Name)%>%
  group_by(City_Name)%>%
  group_by(Year)%>%
  mutate(avgS=mean(Avg_SO2),
         avgCO=mean(Avg_CO),
         avgO3=mean(Avg_O3),
         avgNO2=mean(Avg_NO2),
         avgT=mean(Avg_T),
         avgRH=mean(Avg_RH)
  )
#1
`ggplot()+
  geom_line(mapping=aes(x=Year,y=avgRH),data=data_f,color='red')`+
  xlab("Years")+
  ylab("Relative Humidity")+
  ggtitle("Fluctuation of RH over years")+
  theme(plot.title = element_text(hjust = 0.5))

```

Sample analysis:
a <- ggplot(wdata, aes(x = weight))
```{r}
data_2<-data %>%
  mutate(n_tot=num_x+num_x_1+num_y_1+num_x_2+num_y_2)
ggplot()+
  geom_histogram(mapping=aes(num_x_2),data=data_2,bins=30)+
  xlab("Samples of SO2")+
  ylab("Count")+
  ggtitle("Histogram of SO2 samples")+
  theme(plot.title = element_text(hjust = 0.5))
```

Level-Log Model:
```{r}
levellog_T<-lm(log(Avg_T)~Avg_CO+Avg_NO2+Avg_O3+Avg_SO2+Year+Month+State_Name,data=data)
summary(levellog_T)
write.csv( tidy(levellog_T) , "coefs3.csv" )
```
.
```{r}
levellog_RH<-lm(log(Avg_RH)~Avg_CO+Avg_NO2+Avg_O3+Avg_SO2+Year+Month+State_Name,data=data)
summary(levellog_RH)
write.csv( tidy(levellog_RH) , "levellogrh.csv" )
```
#write.csv( tidy(levellog_RH) , "levellogrh.csv" )
.
```{r}

loglog_RH<-lm(log(Avg_RH+0.0001)~log(Avg_CO+0.0001)+log(Avg_NO2+0.0001)+log(Avg_O3+0.0001)+log(Avg_SO2+0.0001)+log(Year)+Month+State_Name,data=data)
summary(loglog_RH)
```

```{r}

bc <- boxcox(levellog_T,
data = data,
family = "yjPower")
```
Fitting samples
```{r}
s4<-lm(num_x_2~State_Name,data=data_f)
write.csv( tidy(s4) , "pollutant4.csv" )
```

